Dish: Distribution-oblivious Shell Scripting

### 2019-11-22 pldi/draft.tex
Add intro to eval

\section{Evaluation}

@@

>>>>

\section{Evaluation}
\label{eval}

@@

At a high level, we are interested in understanding whether \sys can indeed scale pipelines out automatically and correctly.
To achieve this, we use a combination of micro- and macro-benchmarks, most of which were collected from prior literature and online repositories.
Micro-benchmarks~\sx{micro} are one-off, simple one-line pipelines that take a few seconds to write (usually interactively);
  such pipelines are usually composed interactively to solve a task at hand, test a hypothesis, or ``smoke out bugs''~\cite{bentley1986literate}---but, with \sys, applied to very large data sets.
These pipelines are taken from real, often striking~\cite{}, use cases and have the benefit of highlighting stress on a handful of stages, precisely due to their small size.

Three complex macro-benchmarks (\S\ref{macro1}--\ref{macro3}) involve third-party commands and handle realistic workloads by today's standards.
These scripts are about an order of magnitude larger than the micro-benchmarks, but this perceived lack of complexity is deceiving:
  as shown below, if written in conventional languages, these pipelines would correspond to programs on the order of hundreds of lines of code.

Several results are worth highlighting.
First and foremost, programs see a significant speedup, often more $10\times$ over sequential execution  while returning identical results (on very large datasets).
\sys's transformation and planning phase take around XX--XXms, negligible (XX\%) for short-running pipelines and virtually non-existent for long-running ones.
As \sys rewrites to highly-optimized shell primitives rather than using a managed language runtime, it always has a COST~\cite{mcsherryscalability} of 2.
Finally, \sys preserves the productivity of the shell:
  in one case, the equivalent program for a small part of the pipeline requires over a 150 lines of code in combined Java and Bash to run distributed on top of Hadoop;
  in another, the program expressed by the pipeline was the subject of a semester project in a graduate course on distributed systems~\cite{blinded} where student implementations ranged between 1--3\textbf{K} lines of code.

Experiments were run on a \todo{network of five workstations} connected by 1Gbps links: 
 one large machine (\wka) with 512GB of memory and 128 2.1GHz Intel Xeon E5-2683 cores, and 
 \todo{four smaller machines (\wkq), each with 4GB of memory and two 3.33GHz Intel Core Duo E8600 processors}.
For our software setup, we use SMP Debian 4.9.144-3.1 (2019-02-19), GNU Core-utils 8.30-3, GNU Bash 5.0.3(1)-release (x86\_64-pc-linux-gnu), Python 3.7.3, and OCaml 4.05.0.
Generally, no special configuration was made in hardware or software beyond disabling hyper-threading. % ---specifically, the network protocol stack was left unoptimized.
More detailed setup and experiments, including the scripts, is included in the accompanying (anonymized) online repository.
